Trade Reviews

### 2019-04-12 rosterReview_01.Rmd
Cross-platform solution for cleaning accents, import fixes

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(glue)
library(plotly)
source("R/z_scores.R")
source("R/yahoo_api.R")
```

@@

  draft_results <- read_tsv("data/draftResults.tsv") %>% 
    clean_names() %>% 
    mutate(player = chartr("áéóíñú", "aeoinu", player)) %>% 
    select(pick, player)

@@

#free agents missing display position - not getting free agents from Yahoo

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(glue)
library(plotly)
library(stringi)
source("R/z_scores.R")
source("R/yahoo_api.R")
```

@@

  draft_results <- read_tsv("data/draftResults.tsv") %>% 
    clean_names() %>% 
    mutate(player = stri_trans_general(player, "latin-ascii")) %>% 
    select(pick, player)

@@

@@

```{r}
players <- get_players() %>% 
  clean_names() %>% 
  mutate(name_full = stri_trans_general(name_full, "latin-ascii"))

View(players)
```

### 2019-04-12 tradeReview.Rmd
Cross-platform solution for cleaning accents, import fixes

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(glue)
library(plotly)
```

@@

#### Fantasy team rosters
```{r}
source("R/yahoo_api.R")
get_team_rosters() -> rosters
```

@@

draft_results <- draft_results_raw %>% 
  mutate(player = chartr("áéóíñú", "aeoinu", player)) %>% 
  select(pick, player)
```

#### Join data
```{r}
projections <- proj_batter %>% 
  bind_rows(proj_pitcher)

@@

rosters_with_projections %>% 
  saveRDS("data/rosters_with_projections_20190405.Rds")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(glue)
library(plotly)
library(stringi)
```

@@

@@

draft_results <- draft_results_raw %>% 
  mutate(player = stri_trans_general(player, "latin-ascii")) %>% 
  select(pick, player)
```

#### Join with roster data
```{r}
if (!file.exists("data/rosters_with_projections_20190405.Rds")) {
  source("R/yahoo_api.R")
  get_team_rosters() -> rosters

  projections <- proj_batter %>% 
    bind_rows(proj_pitcher)

@@

  rosters_with_projections %>% 
    saveRDS("data/rosters_with_projections_20190405.Rds")
} else {
  rosters_with_projections <- readRDS("data/rosters_with_projections_20190405.Rds")
}
